\documentclass[11pt]{amsart}
\usepackage{geometry}           % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}              % ... letterpaper or a4paper or a5paper or ... 
%\geometry{landscape}           % Activate for for rotated page geometry
\usepackage[parfill]{parskip}   % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{%
    \noexpand\epstopdfcall{convert #1 \noexpand\OutputFile}%
}

\usepackage{cite}
\usepackage{hyperref}
\usepackage[modulo]{lineno}
\linenumbers

\title{Towards an Online Analysis for Defocusing Micro Particle Tracking Velocimetry}
\author{C. Miao and A. Lewkowicz and M. Vogelgesang and T. Dritschler and S. Chilingaryan and A. Kopmann and P. Cavadini and H. Weinhold}
\address{Karlsruhe Institute of Technology, Postfach 3640, D-76021 Karlsruhe, Germany}
\date{2.7.2015}                     % Activate to display a given date or no date

\begin{document}
\maketitle

\begin{abstract}

At KIT a new micro-PIV setup is currently developed.  It is intended to analyze
flow field in thin films. 

Defocusing particle tracing is able to detect the position of traced particles
in a certain volume around the focal plane. The setup exploits this technique
and used unto five planes in parallel. 

In order to evaluate the experiments and to enable feedback control online
reconstruction is currently developed. Lastest advances in parallel computing
might give rise accelleration factors up to the real-time domain. 

The article will present hardware and software environment and present a
detailed analysis of off-focus PIV algorithms. Latest benchmark results of the
project are presented.

\smallskip
\noindent \textbf{Keywords.} Online Monitoring, GPU Computing, Defocusing PIV, 
Hough Transform, Statistical
\end{abstract}

\include{1-introduction}
\include{2-algorithm}


\end{document}
